---
author: "Gilverto De Los Santos Rios"
output: html_document
source: https://www.kaggle.com/datasets/iabhishekofficial/mobile-price-classification/data 
---


# Importing libraries
```{r}
library(randomForest)
library(caret)
```


# Load data
```{r}
TrainSet = read.csv("train.csv", header = TRUE)
head(TrainSet)
TestingSet = read.csv("test.csv", header = TRUE)
head(TestingSet)
```

# Multiple Linear Regression Model
In order to increase the accuracy of the model, I used a multiple regression model to
determine which characteristics are the most significant against the price_range.
Using the lm() function I was able to create a linear regression model and using the summary() function I can see the significance of each column. There were six values that had a significance value of less the 5% and those will be the only columns I will use.
```{r}
fit = lm(price_range ~., data = TrainSet)
summary(fit)
```

# Clean Data
```{r}
TestingSet$id = NULL 
```

# Building Random Forest Model
```{r}
model = randomForest(as.factor(price_range) ~ battery_power + int_memory + mobile_wt + px_height + px_width +ram, data = TrainSet, ntree = 500, importance = TRUE)
```

# Save Model
Here we can see that the error rate is 8.3% which is lower than a previous model that used all the columns and resulted in a error rate of 11.15%
```{r}
saveRDS(model, "models2.rds")
model
```

